*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-22 Code/Manuscript_O2.Rmd
Materials & Methods edits

@@

## MetaProteomics bioinformatic analyses and limitations  {.unnumbered}

Metaproteomic datasets were obtained from the KM1128 entry in the BCO-DMO database (https://www.bco-dmo.org/deployment/59053) accessed via the OPP in June 2019. Datasets contained:
	i) Peptide sequences and sample identification (ID) number;
	ii) Sample ID number, station, depth in meters below the surface the sample was collected at, best-hit BLASTP protein and species annotation and the corresponding Uniprot Entry number for the identified proteins;
	iii) Sample station depth and [O~2~].  
	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using the Tidyverse package [@R-tidyverse] in RStudio v1.2.5019 (https://rstudio.com/)  (LOCATION OF CODE ON GITHUBO. The resulting merged dataset was filtered for those *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b6f (Cytb6f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Terminal Oxidase (PTOX); plastocyanin (PC); ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  ATP Synthase;  FtsH proteases (FtsH) or ribosomes. 
	Detected peptides were re-annotated for consistency and labelled, where feasible, according to strain, clade, subunit and protein complex . Full protein sequences corresponding to detected proteins were obtained from UniProt (https://www.uniprot.org/) and analyzed in Molecular Evolution and Genetic Analyses X (MEGAX) software  (https://www.megasoftware.net/). Sequences for proteins for each of the thirteen Prochlorococcus strains identified in the dataset were aligned with MUSCLE using UPGMA cluster method and a lambda of 24 with a -2.9 gap open penalty and 1.20 hydrophobicity multiplier.  Overall mean pairwise distance between protein sequences was determined using bootstrap variance estimation methods. Maximum likelihood phylogenetic trees were assembled using 1000 bootstrap replications with a 95% site coverage cut off. *Prochlorococcus* FtsH isoform identities, and inferred functions, were specified by phylogenetic comparison to the characterized FtsH proteases of Synechocystis sp. PCC6803 (CITATONS).  Data for each strain was plotted against depth and  [O~2~] and sampling station.

When assessing the presence of a particular protein complex at a sampling location, all peptides belonging to all subunits of the complex were included to give the greatest number of data points. As this data was acquired on a discovery mission rather than through targeted peptide approaches, it is difficult to discern accuracies of strain assignment annotations, particularly as the proteins of interest in this study are highly conserved across strains. We are, however, confident in clade classifications for each protein examined.
Another caveat to interpretation of this data is the peptide detection bias inherent to mass spectrometry CITATION. The data is also limited by the number and nature of protein spectra in the SEQUEST database: a peptide sequence was not determined unless there is already a known spectrum for that peptide in the SEQUEST database, hence some peptides of interest may not be identifiable. Furthermore, a peptide must be detected above a certain threshold abundance in order to be considered an accurate ‘hit’.

## Growth data management and analysis {.unnumbered}
Data files (.csv) saved from the Multicultivator software were imported into R-Studio [@R-Studio] for data management [@R-tidyverse], growth rate calculations CITATION, comparisons of model fits (get Platt CITATION), and generation of
figures using `ggplot2` [@R-ggplot2]. The chlorophyll proxy
optical density (OD680 - OD720;  ΔOD) was used to determine the chlorophyll-specific exponential growth
rate (µ, d^-1^) for each treatment combination.  We first we used a rolling mean from the RStudio `zoo` package [@R-zoo] to calculate the average ΔOD data over a 1-hour window, to lower influence of outlier points and remove data points collected during post stationary phase, if applicable. We used the Levenberg-Marquardt algorithm
[@bellaviaLevenbergMarquardtMethod2018] modification of the non-linear
least squares,  using the R package `minpack.lm`
[@R-minpack.lm], to fit a logistic
equation \@ref(eq:GrowthRate) where ΔOD~max~ is maximum ΔOD, ΔOD~min~ is minimum ΔOD, t is time
duration over the growth trajectory.  Annotated code for data import, transformations and analyses is available at XXXXX 
CITAtIONS of github locations of code etc. XXXXX

OTHER MOREXXXXXX

### Generalized additive model of growth responses {.unnumbered}

@@

### Estimation of photosynthetically usable radiation {.unnumbered}

@@

### Quantitative protein immunoblotting {.unnumbered}

@@

@@

Proteins derived from Clade HLXXX ecotypes of *P. marinus* were detected in OMZ at depths up to 200 meters,  with O~2~ of 15 µM. The extent to which [O~2~] defines
the niches occupied by different *P. marinus* ecotypes, as compared to
potentially covarying environmental variables like photoperiod, light
spectrum, and light level, is poorly described.

@@

## *Prochlorococcus marinus* growth responses to photoperiod, PAR, spectral bands,  and O~2~  {.unnumbered}

>>>>

## MetaProteomics bioinformatic analyses  {.unnumbered}

Metaproteomic datasets were obtained from the KM1128 entry in the BCO-DMO database (https://www.bco-dmo.org/deployment/59053) accessed via the OPP in June 2019. Datasets contained:
	i) Peptide sequences and sample identification (ID) number;
	ii) Sample ID number, station, depth in meters below the surface the sample was collected at, best-hit BLASTP protein and species annotation and the corresponding Uniprot Entry number for the identified proteins;
	iii) Sample station depth and [O~2~].  
	The depth and [O~2~] were joined to peptide sequence and BLASTP annotations by ID number, depth and station using the Tidyverse package [@R-tidyverse] in RStudio v1.2.5019 (https://rstudio.com/)  (LOCATION OF CODE ON GITHUBO. The resulting merged dataset was filtered for those *Prochlorococcus* peptides, detected from 0 to 300 m below the surface, annotated as a subunit of *Prochlorococcus* chlorophyll binding proteins (Pcb); Photosystem II (PSII); Cytochrome b6f (Cytb6f);  Photosystem I (PSI); NADPH Dehydrogenase (NDH); Terminal Oxidase (PTOX); plastocyanin (PC); ferredoxin (Fd); Ribulose-1,5-bisphosphate oxygenase (RUBISCO);  ATP Synthase;  FtsH proteases (FtsH) or ribosomes. 
	Detected peptides were re-annotated for consistency and labelled, where feasible, according to strain, clade, subunit and protein complex. Full protein sequences corresponding to detected proteins were obtained from UniProt (https://www.uniprot.org/) and analyzed in Molecular Evolution and Genetic Analyses X (MEGAX) software  (https://www.megasoftware.net/). Sequences for proteins for each of the thirteen Prochlorococcus strains identified in the dataset were aligned with MUSCLE using UPGMA cluster method and a lambda of 24 with a -2.9 gap open penalty and 1.20 hydrophobicity multiplier.  Overall mean pairwise distance between protein sequences was determined using bootstrap variance estimation methods. Maximum likelihood phylogenetic trees were assembled using 1000 bootstrap replications with a 95% site coverage cut off. *Prochlorococcus* FtsH isoform identities, and functions, were inferred by sequence comparisons to the characterized four isoforms of FtsH protease of *Synechocystis* sp. PCC6803 (CITATONS).  Data for each strain was plotted against depth and  [O~2~] and sampling station.

When assessing the presence of a particular protein complex at a sampling location, all peptides belonging to all subunits of the complex were included to give the greatest number of data points. As this data was acquired on a discovery mission rather than through targeted peptide approaches, it is difficult to discern accuracies of strain assignment annotations, particularly as the proteins of interest in this study are highly conserved across strains. We are, however, confident in clade classifications for each protein examined. A caveat to interpretation of this data is the peptide detection bias inherent to mass spectrometry CITATION. The data is also limited by the number and nature of protein spectra in the SEQUEST database: a peptide sequence was not determined unless there is already a known spectrum for that peptide in the SEQUEST database, hence some peptides of interest may not be identifiable. Furthermore, a peptide must be detected above a certain threshold abundance in order to be considered an accurate ‘hit’.

@@

## Growth rate analysis {.unnumbered}
Data files (.csv) saved from the Multicultivator software were imported into R-Studio [@R-Studio] for data management [@R-tidyverse], growth rate calculations CITATION, comparisons of model fits (get Platt CITATION), and generation of
figures using `ggplot2` [@R-ggplot2]. The chlorophyll proxy
optical density (OD680 - OD720;  ΔOD) was used to determine the chlorophyll-specific exponential growth
rate (µ, d^-1^) for each treatment combination.  We first we used a rolling mean from the RStudio `zoo` package [@R-zoo] to calculate the average ΔOD data over a 1-hour window, to lower influence of outlier points and remove data points collected during post stationary phase, if applicable. We used the Levenberg-Marquardt algorithm
[@bellaviaLevenbergMarquardtMethod2018] modification of the non-linear
least squares,  using the R package `minpack.lm`
[@R-minpack.lm], to fit a logistic
equation \@ref(eq:GrowthRate) where ΔOD~max~ is maximum ΔOD, ΔOD~min~ is minimum ΔOD, t is time
duration over the growth trajectory.  Annotated code for data import, transformations and analyses is available at XXXXX 
CITAtIONS of github locations of code etc. XXXXX

## Generalized additive model of growth responses {.unnumbered}

@@

## Estimation of photosynthetically usable radiation {.unnumbered}

@@

## Quantitative protein immunoblotting {.unnumbered}

@@

## Naaman GENOMICS METHODS
XXX

@@

XXXMore TextXXX from AuroraXXX
Proteins derived from Clade HLXXX ecotypes of *P. marinus* were detected in OMZ at depths up to 200 meters,  with O~2~ of 15 µM. The extent to which [O~2~] defines
the niches occupied by different *P. marinus* ecotypes, as compared to
potentially covarying environmental variables like photoperiod, light
spectrum, and light level, is poorly described.

@@

## *Prochlorococcus marinus* growth responses to photoperiod, PAR, spectral band, and [O~2~]  {.unnumbered}
